DeepPicar:​ ​A​ ​Low-cost​ ​Deep​ ​Neural​ ​Network-based​ ​Autonomous​ ​Car

### 2017-10-03 paper/evaluation.tex
Fix evaluation typos

\subsection{Multicore Performance}
It may not always be the case that all four cores of the Raspberry Pi 3's Cortex A-53 CPU can be used 
solely for the purpose of operating an autonomous vehicle. Thus, we test how the number of cores 
utilized for real-time operations affects the Pi's overall ability to function as an autonomous 
vehicle platform.

@@

The presence of the benchmark(s) had a noticable effect on the DeepPicar, with all tests showing 
increases in inferencing operations. The least change happened when the model was run on 3 cores, and a 
single benchmark was run on the final core. Even with a slight increase in the number of L2 cache 
misses, inferencing was able to be completed in under 100 ms. The other tests, however, showed dramatic 
changes when the model was run on 1 and 2 cores. In both instances, L2 misses rise to $\sim$23\% of all 
references. The additional benchmark in the 1 core test was even more detrimental as the average 
inferencing time was at least 150 ms longer than when the model used 2 cores.

>>>>

\subsection{Multicore Performance}
It may not always be the case that all four cores of the Raspberry Pi 3's Cortex A-53 CPU can be used 
solely for the purpose of operating an autonomous vehicle. Thus, we test how the number of cores 
utilized for real-time operations affects the DeepPicar's overall ability to function as an autonomous 
vehicle platform.

@@

The presence of the benchmark(s) had a noticable effect on the DeepPicar, with all tests showing 
increases in inferencing operations. The least change happened when the model was run on 3 cores, and a 
single benchmark was run on the final core. Even with a slight increase in the number of L2 cache 
misses, inferencing was able to be completed in under 100 ms. The other tests, however, showed dramatic 
changes when the model was run on 1 and 2 cores. In both instances, L2 misses rose to $\sim$23\% of all 
references. The additional benchmark in the 1 core test was even more detrimental as the average 
inferencing time was at least 150 ms longer than when the model used 2 cores.
